### 2024-11-25 analysis/preprocessing.qmd
fix(preprocessing): recover coutinho2017sh in r_studies

```
2024-10-21: Update studies with multiple unique_ids due to multiple stats reported
```{r}
metaMER_results <- metaMER_results |> 
  dplyr::filter(!(citekey == "zhang2017fe" & statistic == "mean"),
         !(citekey == "zhang2016br" & statistic == "mean"),
         !(citekey == "zhang2016br" & is.na(values)),
         !(citekey == "coutinho2017sh" & statistic == "ccc"),
         # Include only results for energy arousal
         !(citekey == "wang2022cr" & dimension == "tension arousal"),
         !(citekey == "wang2021ac" & dimension == "tension arousal"),
         !(citekey == "deng2015em" & dimension == "resonance"))
```
Deal with repeated experiment IDs in `hu2017cr`
```{r}

>>>>

```
2024-10-21: Update studies with multiple unique_ids due to multiple stats reported
```{r}
metaMER_results <- metaMER_results |> 
  dplyr::filter(!(citekey == "zhang2017fe" & statistic == "mean"),
         !(citekey == "zhang2016br" & statistic == "mean"),
         !(citekey == "zhang2016br" & is.na(values)),
         !(citekey == "coutinho2017sh" & measure == "ccc"),
         # Include only results for energy arousal
         !(citekey == "wang2022cr" & dimension == "tension arousal"),
         !(citekey == "wang2021ac" & dimension == "tension arousal"),
         !(citekey == "deng2015em" & dimension == "resonance"))
```
Deal with repeated experiment IDs in `hu2017cr`
```{r}
